Age-related changes in plant growth and traits

### 2016-11-24 scripts/Accessory_figs_20160905.Rmd
work on accessory costs

```{r}
pdf("ms/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
plot

par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
options(scipen = 5)

mod2 <- sma(scaled_seed_count ~ success_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
mod1 <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])

plot(scaled_ovule_count ~ pollen_attract_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,500),ylab="scaled count",xlim=c(.01,5000),cex=1.5)
points(scaled_seed_count ~ success_costs, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod1,3)
line_function_log_xy(SummarySpp[["mean"]]$success_costs,mod2,1)
#points(scaled_seed_count ~ embryo_endo_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
#arrows(SummarySpp[["mean"]]$success_costs,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)

@@

#discarded costs correlated with seedsize
mod <- sma(discarded_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
summary(mod)
plot(discarded_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

@@

@@

#Table Supplementary.correlations between repro inv and propagule inv by species
```{r}
yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")

@@

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b",2,1)

@@

#panel a
plot(scaled_seed_count~success_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
points(scaled_reach_flowering_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)

@@

mod_seed <- sma(scaled_seed_count~success_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
mod_ovule2 <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
mod_ovule <- sma(scaled_reach_flowering_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])

line_function_log_xy(SummarySpp[["mean"]]$success_costs,mod_seed,1,col=venetian_red)
line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
extra.top.left.logxy("a",2,1)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,300000), xlab="",ylab="",lty=results$linetype,pch=16)
abline(0,1)
mod <- sma(embryo_endo_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
mtext(text="total propagule investment (mg)",side=1,line=2.2,outer=FALSE)
mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
extra.top.left.logxy("a",2,1.2)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
axis(2, at=c(1,100,10000),labels=c("","",""))
abline(0,1)
mtext(text="flower weight * bud count (mg)",side=1,line=2.2,outer=FALSE)
extra.top.left.logxy("b",2,1.2)

>>>>

plot(seedset~scaled_provisioning_costs,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)

mod_ovule <- sma(choosiness~prop_pollen_attract_vs_success,data=SummarySpp[["mean"]],log="xy",method="SMA")

mod_x <- sma(accessory_inv~embryo_endo_inv,data=SummarySpp[["mean"]],log="xy",method="SMA")
mod_x <- sma(accessory_costs~embryo_endo_costs,data=SummarySpp[["mean"]],log="xy",method="SMA")
plot(zygote_set~embryo_endo_costs,SummaryInd,pch=16,log="x",col=col.spp(species),cex=1)

@@

#RESULTS - seed set vs seed size
mod <- sma(seedset ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
summary(mod)
plot(seedset ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

@@

mod <- sma(repro_inv ~ embryo_endo_inv, SummaryInd,method="SMA", log="xy",slope.test=1)
summary(mod)
plot(repro_inv ~ embryo_endo_inv, SummaryInd,log="xy",pch=16,col=col.spp(species))

mod <- sma(repro_inv ~ flower_inv, SummaryInd,method="SMA", log="xy",slope.test=1)
summary(mod)
plot(repro_inv ~ flower_inv, SummaryInd,log="xy",pch=16,col=col.spp(species))

@@

#Table Supplementary.correlations between repro inv and propagule inv by species
```{r}
mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
mod_propagule_inv_all

mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
mod_flower_inv_all

yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")

@@

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b",2,1)

@@

#panel a
plot(scaled_seed_count~repro_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
points(scaled_reach_flowering_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)

@@

mod_seed <- sma(scaled_seed_count~repro_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
mod_ovule2 <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
mod_ovule <- sma(scaled_reach_flowering_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])

line_function_log_xy(SummarySpp[["mean"]]$repro_costs,mod_seed,1,col=venetian_red)
line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
legend("bottomleft",legend=c("seed count by reproductive costs","mature ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
extra.top.left.logxy("a",2,1)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(.3,300000),xlim=c(.3,300000), xlab="",ylab="",lty=results$linetype,pch=16)
abline(0,1)
mod <- sma(embryo_endo_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
mtext(text="total embryo and endosperm investment (mg)",side=1,line=2.2,outer=FALSE)
mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
extra.top.left.logxy("a",2,1.2)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(.3,300000),xlim=c(.3,300000),yaxt="n")
axis(2, at=c(1,100,10000),labels=c("","",""))
abline(0,1)
mtext(text="flower weight * bud count (mg)",side=1,line=2.2,outer=FALSE)
extra.top.left.logxy("b",2,1.2)
